NumPy---Array Programming in Python

### 2020-01-25 paper.tex
Acknowledge larger community

@@

%C.R.H and T.E.O.
S.J.v.d.W and K.J.M. composed the manuscript with input from others.
S.B., K.S., T.J.R., W.W., and M.B. drafted sections.
All authors have contributed significant code, documentation, and/or expertise
to the NumPy project.
All authors reviewed the manuscript.

>>>>

We would also like to thank the many members of the community who have provided
feedback, submitted bug reports, made minor improvements to the documentation,
code, or website, promoted its use in their scientific fields, and built
the vast ecosystem of tools and libraries around NumPy.

@@

%C.R.H and T.E.O.
K.J.M. and S.J.v.d.W composed the manuscript with input from others.
S.B., K.S., T.J.R., W.W., and M.B. drafted sections.
All authors have contributed significant code, documentation, and/or expertise
to the NumPy project.
All authors reviewed the manuscript.
